---
title: "Normal Distribution"
author: "William Namm"
date: "4/5/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
We will be investigating an example of a random normal distribution in R and how to make a histogram out of it.

## Creating the Data Set
First, we use the set.seed() function to define the seed for the random number generator.
This will produce consistent results among different runs of the program.
Then, we use the rnorm() function to create the data set within the norm.dist variable.
```{r}
set.seed(537)
norm.dist <- floor(rnorm(n=50, mean=30, sd=7))
norm.dist
```
The floor() function rounds the numbers down to easily-manageable integers.

## Displaying the data
The data can be displayed as a histogram via the following code:
```{r}
hist(norm.dist)
```
  
We can change the title with the main argument and the axis labels with xlab and ylab arguments. Here is an example:
```{r}
hist(norm.dist, main="Normal Distribution", xlab="Data Points")
```
  
From the graph, we can see that this particular data set roughly follows a normal distribution.
However, it has some positive skew.